\documentclass[12pt,letterpaper]{article}

\usepackage{array}
\usepackage[inline]{enumitem} 
\usepackage{amssymb,amsmath,tabu}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{hyperref}

\begin{document}
\begin{center}
\textbf{Getting Started With Student VR Projects\\for Meneely 201 lab\\Revision 1.0}\\2019-02-12\\Noah Cowie\end{center}
\par To start using a VR student project, you first need its URL. For example, 
\underline{\href{http://groomble.com/temp2018/cartography/gallery.html}{http://groomble.com/temp2018/cartography/gallery.html}}
is a draft version of the gallery developed as part of the cartography project.

\par Then, you will need to do the following steps \textit{in order} to ensure that the controllers are recognized. This may become
unnecessary at a later date (and FireFox release).
\begin{enumerate}
	\item Retrieve both controllers from the corner of the room. They should display green lights until unplugged.
	\item Hold the bottom button (looks like two stacked squares) on each controller until it beeps.
	\item Start Steam, and sign in with the imagine grant credentials on the desk. 
	\item In the main Steam window, click the 'VR' button in the top right.
	\item Wait for SteamVR to open. There should be five green icons for the headset, controllers, and base stations.
	\item Now, open FireFox nightly (which should be on the desktop).
	\item Open your URL in FF nightly.
	\item Click the headset button in the bottom right corner of the browser window.
\end{enumerate}
\end{document}
